\chapter{Networking \& Distributed Computing}
\section{Distributed Computing}
\subsection{System Design}
\subsubsection{Facebook Friends}
Design a system like friend's functionality in facebook. should have all features of facebook's friends functionality. like for each person , he can have any number of friends , 
he will get suggestions for new firends , showing common friends if we visits any other profile . algo should be scalable , robust.

Basically a friends network is an undirected graph. Each person is a vertex of the graph and friendship is an edge between the two vertices. We can represent the graph by by 
maintaining an adjacency list. 
- Like: Each person maintains a list of Posts. Lets say person A puts a post, persons who are connected to person A will be notified about the post (observer pattern). Friend B 
can like a post which increase the 'Like' count. 
- Friends Suggestion: For person A find all nodes X that is at distance 2 from node A. (Now this is scalable as the requirements can tell what is the depth we want to look for 
making suggestions.) 
- Common Friends: When A visits person B. Find all nodes X that are at distance 1 from node A.
- Tagging Friends: 

\subsubsection{REST API}
Design an architecture for REST APIs where you have to upload big data like images/videos etc. Request should be async. Follow up: How will you tune the performance if you have 
millions of requests coming at same time? Clues: Queueing the request, Storing data in filesystems rather than traditional DB etc.

\subsubsection{SWMR}
Design a distributed keystore with a single write end-point and multiple read end-points.


\subsubsection{Phrase Search}
How does a search engine perform exact phrase search? i.e. search for the term "the bees knees" exactly.

When a phrase search is done, there could be multiple ways based on how the search engine is implemented. Will explain one way here. 
Each of the words of the phrases are searched on the inverted index and the posting lists of the corresponding words will all be retrieved. We can do a repeated intersection of 
the sets of documents in the posting lists.. 
In the document set where all the words are present, a more detailed search for the specific location of the word in the documents where each of these words occur. The result will 
have those documents that have them in the consecutive positions in each of the documents in the specified order. 
Sometimes the phrases may be stored as they are too.. For instance to search phrases like "To be or not to be", which consists of all stopwords.. 
If the n gram frequencies in words or phrases are stored as in vector space models, phrase searches are simpler.

\subsubsection{Caching Design}

Design a collaborative text editor where each participant has infinite undo/redo. Consider the scenario where a user goes offline and then comes online and tries to undo/redo.

At a high level very naive approach: each participant generates a string of actions associated with a timestamp. It's a product design decision whether to use client side 
timestamps or server side timestamps for each action. From the server side, it's a matter of merging these action sorted by timestamp. Every participants series of actions are 
stored, so every time participant sends an undo or redo update that action with the latest timestamp (so that it's the latest action now). Action is defined as a character 
(including backspace and cursor move)

When user goes offline, the client side should gray out the document and make it read-only otherwise there's no logical way to merge his changes made in old document to the new 
document when he get online. 

\subsubsection{Parallel BFS and DFS}
Design a parallel Breadth First Search algorithm for a directed weighted graph. 

Basically you need to find the minimum cost to reach to a node from the starting node <given>. (Just save the optimum cost and not the optimum path). Calculate and output the 
optimum reachability cost for all the nodes from a given starting point. 

Implement in C with openMP. 

1. How about using DFS or Shortest path first instead. Would these algorithms perform better than BFS with parallel implementation. Yes/No Why?

While implementing BFS, we enque the neighbours of the present node into the queue. Then we deque each of them and again run a BFS on them sequentially. Because we have a parallel 
processing available, we can execute them in parallel instead of sequential. But we need to keep the common information like visited nodes etc with each of the process.

\subsubsection{Scalability}
How to add a counter to www.google.com to track the billionth user.

Assuming all web requests were always from unique users - worst case for computing! Operationally, the web server fleet needs these processes in it: 

1. Accumulatator: Add number of web requests and send to a timebound computing server. Add a random delay to report this stat so that the computing server has time to process 
requests over a period of time. 
2. Stat listener: Fetches the current stat data from a timebound computing server 

The timebound computing server (lets say 600 servers exist, each counts the request data for 6 seconds) and are roundrobined in 1 hr - it's job is to use the time it has to sort 
the requests timestamp wise. It also fetches data from the previous server in roundrobin when it finishes counting, and adds the current fetched data to this list. If it sees a 
crossover of a billion, it can very well know which transaction caused it. 

This can now be sent to the web server thru' the stat listener, and it could choose to update the unique user during his/her next request. 

Alternately, it can be sent to the user's data in the distributed hash table.

\subsubsection{Distributed Time Zone}
While developing a globally distributed web application that needs to manage time records for system internals 
and for end-user usage (e.g. what date/time do i have the appointment?) \\
what best practices would you implement? \\
Hints - Server time versus user time. Distributed servers. Several timezones. Daylight savings time etc.

we can use NTP algorithm to deal with this situation.it uses a hierarchical, semi-layered system of levels of clock sources. 
This algorithm is a class of mutual network synchronization algorithm which allows for use-selectable policy control in the design of the time synchronization and evidence model. 
NTP supports single inline and meshed operating models in which a clearly defined master source of time is used ones in which no penultimate master or reference clocks are needed. 

In NTP service topologies based on peering all clocks equally participate in the synchronization of the network by exchanging their timestamps using regular beacon packets. In 
addition NTP supports a UNICAST type time transfer which provides a higher level of security. NTP performance is tunable based on its application and environmental loading as well.

\subsubsection{Heap vs Stack}
What is the difference between a computers heap and it's stack?

Physically stack and heap both are allocated on RAM and their implementation varies from language, compiler and run time 

Stack is used for local variables of functions and to track function calling sequences. Heap is used for allocating dynamically created variables using malloc, calloc or new. 
Stack memory is freed whenever the function completes execution but the heap memory needs to be freed explicitly using delete, free or by garbage collector of the language. 

Stack memory of a process is fixed size and heap is variable memory. 

Stack is faster than heap as allocating memory on stack is simpler just moving stack pointer up. 

In case of multi threading, each thread of process will have a different stack but all threads share single heap
