\chapter{查找}

\section{折半查找} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{Codex}[label=binary_search.c]
/** 数组元素的类型 */
typedef int elem_t;
/**
  * @brief 有序顺序表的折半查找算法.
  *
  * @param[in] a 存放数据元素的数组，已排好序
  * @param[in] n 数组的元素个数
  * @param[in] x 要查找的元素
  * @return 如果找到 x，则返回其下标。 如果找
  * 不到 x 且 x 小于 array 中的一个或多个元素，则为一个负数，该负数是大
  * 于 x 的第一个元素的索引的按位求补。 如果找不到 x 且 x 大于 array 中的
  * 任何元素，则为一个负数，该负数是（最后一个元素的索引加 1）的按位求补。 
  */
int binary_search(const elem_t a[], const int n, const elem_t x) {
    int left = 0, right = n -1, mid;
    while(left <= right) {
        mid = left + (right - left) / 2;
        if(x > a[mid]) {
            left = mid + 1;
        } else if(x < a[mid]) {
            right = mid - 1;
        } else {
            return mid;
        }
    }
    return -(left+1);
}
\end{Codex}


\section{哈希表} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\subsection{原理和实现}
\label{sec:hash-set}
哈希表处理冲突有两种方式，开地址法(Open Addressing)和闭地址法(Closed Addressing)。

闭地址法也即拉链法(Chaining)，每个哈希地址里不再是一个元素，而是链表的首地址。

开地址法有很多方案，有线性探测法(Linear Probing)、二次探测法(Quodratic Probing)和双散列法(Double Hashing)等。

下面是拉链法的C语言实现。

\subsubsection{代码}
\begin{Codex}[label=hash_set.hpp]
/** 元素的哈希函数  */
template<typename elem_t>
int elem_hash(const elem_t &e);

/** 元素的比较函数  */
template<typename elem_t>
bool operator==(const elem_t &e1, const elem_t &e2);

/** 哈希集合, elem_t 是元素的数据类型. */
template<typename elem_t>
class hash_set {
public:
    hash_set(int prime, int capacity);
    ~hash_set();
    bool find(const elem_t &elem); /** 查找某个元素是否存在. */
    bool insert(const elem_t &elem); /** 添加一个元素，如果已存在则添加失败. */
private:
    int prime; /** 哈希表取模的质数，也即哈希桶的个数，小于 capacity. */
    int capacity; /** 哈希表容量，一定要大于元素最大个数  */

    int *head/*[PRIME]*/; /** 首节点下标 */

    struct node_t {
        elem_t elem;
        int next;
        node_t():next(-1) {}
    } *node/*[HASH_SET_CAPACITY]*/; /** 静态链表 */

    int size; /** 实际元素个数 */
};

template<typename elem_t>
hash_set<elem_t>::hash_set(int prime, int capacity) {
    this->prime = prime;
    this->capacity = capacity;
    head = new int[prime];
    node = new node_t[capacity];
    fill(head, head + prime, -1);
    fill(node, node + capacity, node_t());
    size = 0;
}

template<typename elem_t>
hash_set<elem_t>::~hash_set() {
    this->prime = 0;
    this->capacity = 0;
    delete[] head;
    delete[] node;
    head = NULL;
    node = NULL;
    size = 0;
}

template<typename elem_t>
bool hash_set<elem_t>::find(const elem_t &elem) {
    for (int i = head[elem_hash(elem)]; i != -1; i = node[i].next)
        if (elem == node[i].elem) return true;

    return false;
}

template<typename elem_t>
bool hash_set<elem_t>::insert(const elem_t &elem) {
    const int hash_code = elem_hash(elem);

    for (int i = head[hash_code]; i != -1; i = node[i].next)
        if (elem == node[i].elem) return false; // 已经存在

    /* 不存在，则插入在首节点之前 */
    node[size].next = head[hash_code];
    node[size].elem = elem;
    head[hash_code] = size++;
    return true;
}
\end{Codex}


\subsection{Babelfish}


\subsubsection{描述}
You have just moved from Waterloo to a big city. The people here speak an incomprehensible dialect of a foreign language. Fortunately, you have a dictionary to help you understand them.


\subsubsection{输入}
Input consists of up to 100,000 dictionary entries, followed by a blank line, followed by a message of up to 100,000 words. Each dictionary entry is a line containing an English word, followed by a space and a foreign language word. No foreign word appears more than once in the dictionary. The message is a sequence of words in the foreign language, one word on each line. Each word in the input is a sequence of at most 10 lowercase letters.


\subsubsection{输出}
Output is the message translated to English, one word per line. Foreign words not in the dictionary should be translated as "eh".


\subsubsection{样例输入}
\begin{Code}
dog ogday
cat atcay
pig igpay
froot ootfray
loops oopslay

atcay
ittenkay
oopslay
\end{Code}


\subsubsection{样例输出}
\begin{Code}
cat
eh
loops
\end{Code}


\subsubsection{分析}
最简单的方法是，把输入的单词对，存放在一个数组，排好序，查找的时候每次进行二分查找。

更快的方法是，用HashMap。C++有\fn{map}，C++ 11以后有\fn{unordered_map}，比\fn{map}快。也可以自己实现哈希表。


\subsubsection{代码}
使用 \fn{map} 。

\begin{Codex}[label=babelfish_map.cpp]
/* POJ 2503 Babelfish , http://poj.org/problem?id=2503 */
#include <cstdio>
#include <map>
#include <string>
#include <cstring>

using namespace std;

/** 字符串最大长度 */
const int MAX_WORD_LEN = 10;

int main() {
    char line[MAX_WORD_LEN * 2 + 1];
    char s1[MAX_WORD_LEN + 1], s2[MAX_WORD_LEN + 1];
    map<string, string> dict;

    while (gets(line) && line[0] != 0) {
        sscanf(line, "%s %s", s1, s2);
        dict[s2] = s1;
    }

    while (gets(line)) {
        if (dict[line].length() == 0) puts("eh");
        else printf("%s\n", dict[line].c_str());
    }
    return 0;
}
\end{Codex}


自己实现哈希表。

\begin{Codex}[label=babelfish.cpp]
/* POJ 2503 Babelfish , http://poj.org/problem?id=2503 */
#include <cstring>

/** 单词最大长度. */
#define MAX_WORD_LEN   11

/** 词典中的一对. */
struct dict_pair_t {
    char english[MAX_WORD_LEN];
    char foreign[MAX_WORD_LEN];
};

/** 哈希表容量，一定要大于元素最大个数  */
#define HASH_SET_CAPACITY  100001
/** 哈希表取模的质数，也即哈希桶的个数，小于 HASH_SET_CAPACITY. */
#define PRIME  99997

int elem_hash(const dict_pair_t &e) {
    const char *str = e.foreign;
    unsigned int r = 0;
    int len = strlen(str);
    int i;

    for (i = 0; i < len; i++) {
        r = (r * 31 + str[i]) % PRIME;
    }
    return r % PRIME;
}

bool operator==(const dict_pair_t &e1, const dict_pair_t &e2) {
    return strcmp(e1.foreign, e2.foreign) == 0;
}

/* 等价于复制粘贴，这里为了节约篇幅，使用include，在OJ上提交时请用复制粘贴 */
#include "hash_set.hpp"  /* 见“查找->哈希表”这节 */

/* 跟find()略有不同，专为为本题定制 */
template<typename elem_t>
bool hash_set<elem_t>::get(elem_t &e) {
    for (int i = head[elem_hash(e)]; i != -1; i = node[i].next)
        if (e == node[i].elem) {
            // 多了一行代码，获取对应的 english
            strncpy(e.english, node[i].elem.english, MAX_WORD_LEN-1);
            return true;
        }

    return false;
}


int main() {
    char line[MAX_WORD_LEN * 2];
    hash_set<dict_pair_t> set(PRIME, HASH_SET_CAPACITY);
    dict_pair_t e;

    while (gets(line) && line[0] != 0) {
        sscanf(line, "%s %s", e.english, e.foreign);
        set.insert(e);
    }
    while (gets(e.foreign)) {
        if (set.get(e)) printf("%s\n", e.english);
        else printf("eh\n");
    }
    return 0;
}
\end{Codex}


\subsubsection{相关的题目}
与本题相同的题目：
\begindot
\item POJ 2503 Babelfish, \myurl{http://poj.org/problem?id=2503}
\myenddot

与本题相似的题目：
\begindot
\item  无
\myenddot


\section{Search for a Range} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\label{sec:search-for-a-range}


\subsubsection{描述}
Given a sorted array of integers, find the starting and ending position of a given target value.

Your algorithm's runtime complexity must be in the order of $O(\log n)$.

If the target is not found in the array, return \code{[-1, -1]}.

For example,
Given \code{[5, 7, 7, 8, 8, 10]} and target value 8,
return \code{[3, 4]}.


\subsubsection{分析}
已经排好了序，用二分查找。


\subsubsection{使用STL}
\begin{Code}
	// LeetCode, Search for a Range
	// 偷懒的做法，使用STL
	// 时间复杂度O(logn)，空间复杂度O(1)
	class Solution {
		public:
		vector<int> searchRange(int A[], int n, int target) {
			const int l = distance(A, lower_bound(A, A + n, target));
			const int u = distance(A, prev(upper_bound(A, A + n, target)));
			if (A[l] != target) // not found
			return vector<int> { -1, -1 };
			else
			return vector<int> { l, u };
		}
	};
\end{Code}


\subsubsection{重新实现 lower_bound 和 upper_bound}
\begin{Code}
	// LeetCode, Search for a Range
	// 重新实现 lower_bound 和 upper_bound
	// 时间复杂度O(logn)，空间复杂度O(1)
	class Solution {
		public:
		vector<int> searchRange (int A[], int n, int target) {
			auto lower = lower_bound(A, A + n, target);
			auto uppper = upper_bound(lower, A + n, target);
			
			if (lower == A + n || *lower != target)
			return vector<int> { -1, -1 };
			else
			return vector<int> {distance(A, lower), distance(A, prev(uppper))};
		}
		
		template<typename ForwardIterator, typename T>
		ForwardIterator lower_bound (ForwardIterator first,
		ForwardIterator last, T value) {
			while (first != last) {
				auto mid = next(first, distance(first, last) / 2);
				
				if (value > *mid)   first = ++mid;
				else                last = mid;
			}
			
			return first;
		}
		
		template<typename ForwardIterator, typename T>
		ForwardIterator upper_bound (ForwardIterator first,
		ForwardIterator last, T value) {
			while (first != last) {
				auto mid = next(first, distance (first, last) / 2);
				
				if (value >= *mid)   first = ++mid;  // 与 lower_bound 仅此不同
				else                 last = mid;
			}
			
			return first;
		}
	};
\end{Code}

\subsubsection{相关题目}
\begindot
\item Search Insert Position, 见 \S \ref{sec:search-insert-position}
\myenddot


\section{Search Insert Position} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\label{sec:search-insert-position}


\subsubsection{描述}
Given a sorted array and a target value, return the index if the target is found. If not, return the index where it would be if it were inserted in order.

You may assume no duplicates in the array.

Here are few examples.
\begin{Code}
	[1,3,5,6], 5 → 2
	[1,3,5,6], 2 → 1
	[1,3,5,6], 7 → 4
	[1,3,5,6], 0 → 0
\end{Code}


\subsubsection{分析}
即\fn{std::lower_bound()}。


\subsubsection{代码}
\begin{Code}
	// LeetCode, Search Insert Position
	// 重新实现 lower_bound
	// 时间复杂度O(logn)，空间复杂度O(1)
	class Solution {
		public:
		int searchInsert(int A[], int n, int target) {
			return lower_bound(A, A + n, target) - A;
		}
		
		template<typename ForwardIterator, typename T>
		ForwardIterator lower_bound (ForwardIterator first,
		ForwardIterator last, T value) {
			while (first != last) {
				auto mid = next(first, distance(first, last) / 2);
				
				if (value > *mid)   first = ++mid;
				else                last = mid;
			}
			
			return first;
		}
	};
\end{Code}


\subsubsection{相关题目}
\begindot
\item Search for a Range, 见 \S \ref{sec:search-for-a-range}
\myenddot


\section{Search a 2D Matrix} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\label{sec:search-a-2d-matrix}


\subsubsection{描述}
Write an efficient algorithm that searches for a value in an $m \times n$ matrix. This matrix has the following properties:
\begindot
\item Integers in each row are sorted from left to right.
\item The first integer of each row is greater than the last integer of the previous row.
\myenddot

For example, Consider the following matrix:
\begin{Code}
	[
	[1,   3,  5,  7],
	[10, 11, 16, 20],
	[23, 30, 34, 50]
	]
\end{Code}
Given \fn{target = 3}, return true.


\subsubsection{分析}
二分查找。


\subsubsection{代码}
\begin{Code}
	// LeetCode, Search a 2D Matrix
	// 时间复杂度O(logn)，空间复杂度O(1)
	class Solution {
		public:
		bool searchMatrix(const vector<vector<int>>& matrix, int target) {
			if (matrix.empty()) return false;
			const size_t  m = matrix.size();
			const size_t n = matrix.front().size();
			
			int first = 0;
			int last = m * n;
			
			while (first < last) {
				int mid = first + (last - first) / 2;
				int value = matrix[mid / n][mid % n];
				
				if (value == target)
				return true;
				else if (value < target)
				first = mid + 1;
				else
				last = mid;
			}
			
			return false;
		}
	};
\end{Code}


\subsubsection{相关题目}
\begindot
\item 无
\myenddot
